The Effect of Racial and Ethnic Attitudes on Asian Identity in the U.S

### 2024-09-24 my_paper/manuscript_main.tex
edit push first version

This paper is most closely related to \textcite{antmanEthnicAttritionObserved2016,antmanIncentivesIdentifyRacial2015,antmanAmericanIndianCasinos2021} where the authors studied the ethnic attrition of Asian immigrants and how minorities change their self-reported identity to changes in policies.\footnote{Ethnic attrition is when a person with Asian ancestry fails to self-identify as Asian.} Taking into consideration the ethnic attrition that \textcite{antmanEthnicAttritionObserved2016} document, I investigate the determinants of what drives a person to self-report, or not, their Asian identity. I aim to decompose some of the complexity associated with endogenous identity by exploring certain personal and environmental determinants of identity. The empirical analysis in this paper documents how certain observable factors, namely personal characteristics and societal attitudes, affect the self-reported identity of Asians.

@@

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using both the IAT and the ANES racial animus measure.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the state-level average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}) and the results to the estimation of equation (\ref{eq:identity_reg_bias}) by the proxy respondent in Table (\ref{regtab-proxy-01}) across all generations. The main effect of the reported Asian identity of children is 93 percentage points when the mother is the proxy, 92 percentage points when the father is the proxy, and 96 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.} The estimation of equation (\ref{eq:identity_reg_bias}) by the proxy respondent, Table (\ref{regtab-proxy-01}), mostly yields a negative effect of bias on self-reported Asian identity for all types of proxy respondents.

@@

Another concern could be reverse causality between having more Asian or Black people in a state and bias. It could be the case that the number of Asian people in a state affects the bias on the residents of that state. For example, having more Asians in Florida or Black people in Louisiana could affect the  bias of the residents of Florida and Louisiana. To show that this is not the case, I provide Figures (\ref{scatter-plot-1}), (\ref{scatter-plot-black-1}), and (\ref{scatter-plot-4}) as evidence. Figure (\ref{scatter-plot-1}) plots the percent of self-reported Asians in a state at a specific year against the average  bias in the same state during that year. Figure (\ref{scatter-plot-black-1}) plots the percent of Black in a state at a specific year against. Figure (\ref{scatter-plot-4}) plots the percent of objectively second-generation Asian children of endogamous marriages in a state at a certain year against the average bias in the same state during that year. I find no correlation between bias and the number of Asians in a state, thus, making the case of reverse causality unlikely. There is a slight correlation between percent Black and bias in a state. Consequently, I perform a horse race regression in Table (\ref{regtab-horserace}) to show that the relationship between bias and self-reported Asian identity is not driven by the percent of Black people in a state. Adding percent Black as a control does not change the relationship between bias and self-reported Asian identity.

>>>>

This paper is most closely related to \textcite{hadahforthcominghispanicidentity, antmanEthnicAttritionObserved2016,antmanIncentivesIdentifyRacial2015,antmanAmericanIndianCasinos2021} where the authors studied the ethnic attrition of Hispanic immigrants and how minorities change their self-reported identity to changes in policies.\footnote{Ethnic attrition is when a person with Asian ancestry fails to self-identify as Asian.} Taking into consideration the ethnic attrition that \textcite{antmanEthnicAttritionObserved2016} document, I investigate the determinants of what drives a person to self-report, or not, their Asian identity. \textcite{hadahforthcominghispanicidentity} finds that bias and self-reported Hispanic identity are negatively associates among a sample of objectively Hispanic immigrants. I aim to decompose some of the complexity associated with endogenous identity by exploring certain personal and environmental determinants of identity. The empirical analysis in this paper documents how certain observable factors, namely personal characteristics and societal attitudes, affect the self-reported identity of Asians.

@@

Moreover, to reduce attenuation bias and measurement error, I follow \textcite{lubotskyInterpretationRegressionsMultiple2006} in constructing a composite bias measure using  the IAT, the ANES racial animus measure and hare crimes against Asians.\footnote{More on the method in the Data Online Appendix, see Section~\ref{sub:lw-bias}.} Figure (\ref{fig:skiniat}) shows a graphical representation of the bias measure over time in the most and least biased locations. Figure (\ref{fig:Asian-twostates}) shows a graphical representation of self-reported Asian identity in the two most and least biased locations. A lower score implies less bias, whereas a higher score implies higher racial animus. A one standard deviation increase in bias is equivalent to moving from Washington, DC, or Vermont to North Dakota in 2020. I also show the state-level average bias over time in the maps in Figure (\ref{fig:skiniat-maps}) and the overall average from 2004 to 2021 in Figure (\ref{fig:iat-map-all}).
\section{Estimation and Results}\label{sec:empstrat}

@@

Moreover, \textcite{duncanIntermarriageIntergenerationalTransmission2011} show that reported Asian identification does not vary with who is the household respondent. Additionally, I present the main effect of self-reported Asian identity by the household respondent in Table (\ref{tab:hispbyproxy}). The main effect of the reported Asian identity of children is 93 percentage points when the mother is the proxy, 92 percentage points when the father is the proxy, and 96 percentage points when the child or another caregiver was the household respondent.\footnote{According to the Current Population Survey (CPS), a person can be the household respondent if they are at least 15 years old and have enough knowledge about the household. Thus, when the proxy is 'self,' the respondent is between the ages of 15 and 17.}

@@

Another concern could be reverse causality between having more Asian or Black people in a state and bias. It could be the case that the number of Asian people in a state affects the bias on the residents of that state. For example, having more Asians in Florida or Black people in Louisiana could affect the  bias of the residents of Florida and Louisiana. To show that this is not the case, I provide Figures (\ref{scatter-plot-1}) as evidence. Figure (\ref{scatter-plot-1}) plots the percent of self-reported Asians in a state at a specific year against the average  bias in the same state during that year. I find no correlation between bias and the number of Asians in a state, thus, making the case of reverse causality unlikely.

### 2024-09-24 my_paper/manuscript_online_appendix.tex
edit push first version

\section{Tables}\label{appendix:tabs}

@@

>>>>

\section{Data} % (fold)
\label{sec:data-ap}

\begin{figure}[H]
\centering
\caption{Examples of an Implicit Association Test}
\label{fig:iatexamples}
\begin{subfigure}{.48\textwidth}
\centering
\includegraphics[width=.9\linewidth]{figure/iatexample1.png}
\end{subfigure}
\centering
%Second graph
\begin{subfigure}{.48\textwidth}
\centering
\includegraphics[width=.9\linewidth]{figure/iatexample2.png}
\end{subfigure}
%Third
\begin{subfigure}{.48\textwidth}
\centering
\includegraphics[width=.9\linewidth]{figure/iatexample3.png}
\end{subfigure}
% Fourth
\begin{subfigure}{.48\textwidth}
\centering
\includegraphics[width=.9\linewidth]{figure/iatexample4.png}
\end{subfigure}
%Fifth
\begin{subfigure}{.48\textwidth}
\centering
\includegraphics[width=.9\linewidth]{figure/iatexample5.png}
\end{subfigure}
\caption*{\footnotesize{Here are a few examples of what a respondent would see on an implicit association test.}}
\end{figure}

\newpage
\pagebreak

@@

\begin{figure}[H]
    \centering
    \caption{Scatter Plot of Proportion Subjectively Asian on Bias}
    \label{scatter-plot-1}
    \begin{subfigure}{.9\textwidth}
    \caption{Year < 2015}
    \centering
    \includegraphics[width=.9\linewidth]{figure/scatter-plot-bias-Asian-less2015.png}
    \end{subfigure}
    \centering
    %Second graph
    \begin{subfigure}{.9\textwidth}
    \caption{Year $\geq$ 2015}
    \centering
    \includegraphics[width=.9\linewidth]{figure/scatter-plot-bias-Asian-great2015.png}
    \end{subfigure}
    \caption*{\footnotesize{Here are two scatter plots showing the relationship between bias and subjective Asian population in a state. Each dot represents a state in a certain year. Percent subjectively Asian = $\frac{\# \text{Asian}}{\text{Population}}$ \\
    \emph{Source.} 2004-2021 Current Population Survey.}}
    \end{figure}

### 2024-09-24 my_paper/manuscript_tab_fig.tex
edit push first version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{tables/tab01-SumStat}

@@

@@

\caption*{\footnotesize{In this figure, I show the state-level implicit bias in different years in the sample. Each panel presents state-level bias during a certain year. The boundaries in red represent the different Census divisions in the United States. Notice how there is a variation across states with-in a region.}}
\end{figure}
\end{center}

@@

\input{tables/maineffect-proxy}

@@

\input{tables/maineffect-proxy}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{landscape}
\input{tables/tab01-SumStat}
\end{landscape}

@@

\begin{center}
\begin{figure}[H]
\caption{Diagram of the Three Different Generations of Asian Immigrants.}
\includegraphics[width=\textwidth, height=9cm]{figure/diag.png} 
\label{fig:diag}
\end{figure}
\hfill%
\end{center}

@@

\caption*{\footnotesize{This figure shows the state-level bias index in different years in the sample. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. Each panel presents state-level bias during a certain year. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[H]
\caption{Maps of State-level Bias 2004-2021 Measure with Census Division Regional Boundaries}
\includegraphics[width=\textwidth]{figure/Average_Skinmap.png} 
\label{fig:iat-map-all}
\caption*{\footnotesize{This figure shows the state-level bias index in the sample from 2004 to 2021. The bias units are in standard deviations and ranges from low to high bias. Bias index is constructed following \textcite{lubotskyInterpretationRegressionsMultiple2006}. The data is from the 2004-2021 Harvard's Project Implicit Association Test scores, American National Election Studies (ANES), and state-level hate crimes against Asians. The boundaries in black represent the different Census divisions in the United States. Notice how there is a variation across states within a region.}}
\end{figure}
\end{center}

@@

\input{tables/tab46-iat-migration-tab.tex}

@@

\input{tables/maineffect-proxy}
\pagebreak
\newpage

### 2024-09-24 my_paper/manuscript_title_etc.tex
edit push first version

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian-speaking country. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of implicit ethnic bias. A one standard deviation increase in bias decreases self-reported Asian identity by 7 and 13 percentage points for first and second-generation Asians, respectively. These effects are more prominent among second-generation immigrants with both parents born in an Asian-speaking country than among children of inter-ethnic parents. These findings have implications for the interpretation of research on ethnic gaps in economic outcomes and the correct counting of the population.
    \PAPERJEL}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 5. Define Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\PAPERABSTRACT}{
I study the determinants of the choice to identify as Asian among those who could—those whose parents, grandparents, or selves were born in an Asian country. I find that individuals with Asian ancestry are significantly less likely to self-identify as Asian if they live in states with high levels of implicit ethnic bias. A one standard deviation increase in bias decreases self-reported Asian identity by 9 percentage points for all immigrants. A one standard deviation increase in bias decreases self-reported Asian identity by 8 and 9 percentage points for second- and third-generation Asians respectively. These findings have implications for the interpretation of research on racial and ethnic gaps in economic outcomes and the correct counting of the population.
    \PAPERJEL}
